
---
title: "Untitled"
author: "Author"
date: "2026-05-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
packages <- c("sf", "igraph","ITNr", "wdnet", "dplyr", "plm","ggplot2", "patchwork", "ggraph", "tidygraph", "here", "scales", "ggrepel", "geosphere", "rnaturalearth", "countrycode")
invisible(lapply(packages, function(pkg) {suppressPackageStartupMessages(library(pkg, character.only = TRUE))}))
```

```{r}
m <- read.csv("../data/cleaned/edgelist_stock.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
```

```{r}
cp_function <- function(m, year) {

  ycol <- paste0("X", year)

  m_y <- m[, c("origin", "destination", ycol)]
  m_y <- subset(m_y, m_y[[ycol]] > 0)

  net <- igraph::graph_from_data_frame(m_y, directed = TRUE)
  igraph::E(net)$weight <- igraph::edge_attr(net, ycol)

  cp <- core_periphery_weighted(net, "directed")
  cp_mat <- cp[[2]]
  cp_df <- as.data.frame(cp_mat)

  med_sigma_in <- median(cp_df$sigma_in, na.rm = TRUE)
  med_sigma_out <- median(cp_df$sigma_out, na.rm = TRUE)

  cp_df$median_sigma_in <- med_sigma_in
  cp_df$median_sigma_out <- med_sigma_out

  cp_df$core_3 <- dplyr::case_when(cp_df$in_cp == 1 ~ 1, cp_df$in_cp == 0 & cp_df$sigma_in > med_sigma_in ~ 2, TRUE ~ 3)

  cp_df$core_4 <- dplyr::case_when(
    cp_df$sigma_in > med_sigma_in & cp_df$sigma_out <= med_sigma_out ~ "pure_magnet",
    cp_df$sigma_in <= med_sigma_in & cp_df$sigma_out > med_sigma_out ~ "pure_source",
    cp_df$sigma_in > med_sigma_in & cp_df$sigma_out > med_sigma_out ~ "transition_hub",
    TRUE ~ "periphery")

  sigma <- data.frame(country = igraph::V(net)$name, cp_df, year = year)

  return(list(year = year, network = net, sigma = sigma))}
```


```{r}
years <- 1990:2020

cp_results <- lapply(years, function(y) cp_function(m, y))
names(cp_results) <- years

cp_data <- dplyr::bind_rows(lapply(cp_results, function(x) x$sigma))
```


```{r}
dim(cp_data)
length(unique(cp_data$country))
length(unique(cp_data$year))
colnames(cp_data)
```

```{r}
# Function to compute weighted centrality measures with four different weights on the edges
degree_computation <- function(g1, alphas = c(0, 0.5, 0.8, 1)) {
  results_list <- list()
  for (a in alphas) {
    outdeg <- centrality(g1, measure = "degree", degree.control = list(alpha = a, mode = "out"))
    indeg <- centrality(g1, measure = "degree", degree.control = list(alpha = a, mode = "in"))
    df <- data.frame(node = g1$node.attr$name , alpha = a, outdegree = outdeg, indegree = indeg)
    results_list[[paste0("alpha_", a)]] <- df}
  final_df <- do.call(rbind, results_list)
  rownames(final_df) <- NULL
  return(final_df)
}
```

```{r}
# Function to run the centrality measures on igraph objects
centrality_function <- function(m, year) {
  ycol <- paste0("X", year)
  m_y <- m[, c("origin", "destination", ycol)]
  m_y <- subset(m_y, m_y[[ycol]] > 0)
  net <- igraph::graph_from_data_frame(m_y, directed = TRUE)
  igraph::E(net)$weight <- igraph::edge_attr(net, ycol)
  g <- igraph_to_wdnet(net)
  deg <- degree_computation(g)
  deg_df <- deg %>%
    dplyr::select(-outdegree.name, -indegree.name) %>%
    dplyr::rename(
      country = node,
      out_deg = outdegree.degree,
      in_deg  = indegree.degree
    ) %>%
    dplyr::mutate(year = year)
  
  return(deg_df)
}
  
```

```{r}
# Creating a df with centrality measures
centrality_results <- lapply(years, function(y) {centrality_function(m, y)})

centrality_data <- dplyr::bind_rows(centrality_results)
```

```{r}
dim(centrality_data)
length(unique(centrality_data$country))
length(unique(centrality_data$year))
length(unique(centrality_data$alpha))
#unique(panel_data["year"])
colnames(centrality_data)
```

```{r}
# Merging the cp data with the centrality data
merged <- dplyr::left_join(centrality_data, cp_data, by = c("country", "year"))
```

```{r}
dim(merged)
length(unique(merged$country))
length(unique(merged$year))
length(unique(merged$alpha))
colnames(merged)
```

```{r}
# Soring the data
merged <- merged %>% arrange(country, year, alpha)

# Transforming indegree and outdegree measures into log form
merged <- merged %>% mutate(log_in_deg  = log1p(in_deg),log_out_deg = log1p(out_deg))
```

```{r}
# Separating the countries into four categories based on top quantile of indegree, outdegree and median value of in core and out core. Type_hybrid = "pure magnet" if sigma_in is on top of its highest 25% values, sigma_out is equal or below to its highest 25% values, and in_degree centrality is more than its median. 
# It is "pure source" if sigma_out is within its top 25%, sigma_in is below its lower 75%, and out degree is greater than its median.
# It is a "hub" if both sigma_in and sigma_out are within their top 25% values. 
# All other countries are categorized as "periphery"

merged <- merged %>%
  group_by(year) %>%
  mutate(
    q75_in  = quantile(sigma_in,  0.75, na.rm = TRUE),
    q75_out = quantile(sigma_out, 0.75, na.rm = TRUE),
    med_in_deg  = median(in_deg,  na.rm = TRUE),
    med_out_deg = median(out_deg, na.rm = TRUE),
    
    type_hybrid = case_when(
      sigma_in > q75_in & in_deg > med_in_deg & sigma_out <= q75_out ~ "pure_magnet",
      sigma_out > q75_out & out_deg > med_out_deg & sigma_in <= q75_in ~ "pure_source",
      sigma_in > q75_in & sigma_out > q75_out ~ "hub",
      TRUE ~ "periphery"
    )
  ) %>%
  ungroup()
```

```{r}
table(merged$type_hybrid[merged$year == 1990])
table(merged$type_hybrid[merged$year == 2020])
```
```{r}
#unique(merged$country[merged$year == 1990 & merged$type_hybrid == "periphery"])

summary(merged$sigma_in)
summary(merged$sigma_out)
summary(merged$in_deg)
summary(merged$out_deg)
```

```{r}
write.csv(merged, "../data/cleaned/network_variables.csv")
```



### Making a corridor matrix
```{r}

make_corridor_matrix <- function(m, cp_data, years) {

  ## Keep origin and destination
  corridor_matrix <- m[, c("origin", "destination")]

  for (yr in years) {

    ycol <- paste0("X", yr)

    ## Keep only the CP classification for this year
    cp_year <- cp_data %>%
      filter(year == yr) %>%
      select(country, in_cp)

    ## Join origin and destination CP status
    tmp <- m %>%
      select(origin, destination) %>%
      left_join(cp_year,
                by = c("origin" = "country")) %>%
      rename(in_cp_origin = in_cp) %>%
      left_join(cp_year,
                by = c("destination" = "country")) %>%
      rename(in_cp_destination = in_cp)

    ## Create corridor variable
    corridor_matrix[[ycol]] <- case_when(
      tmp$in_cp_origin == 0 & tmp$in_cp_destination == 0 ~ 1,
      tmp$in_cp_origin == 1 & tmp$in_cp_destination == 0 ~ 2,
      tmp$in_cp_origin == 0 & tmp$in_cp_destination == 1 ~ 3,
      tmp$in_cp_origin == 1 & tmp$in_cp_destination == 1 ~ 4,
      TRUE ~ NA_real_
    )
  }

  return(corridor_matrix)
}
```

```{r}
years <- 1990:2020

corridor_matrix <- make_corridor_matrix(
  m = m,
  cp_data = cp_data,
  years = years
)
```

```{r}
dim(corridor_matrix)

head(corridor_matrix)
```
```{r}
corridor_labels <- c(
  "1" = "PP",
  "2" = "CP",
  "3" = "PC",
  "4" = "CC"
)
```










## Trimming the dataset for the world map

```{r}
# # Defining a country group having the lowest 5% degree centralities as 'low_node'
# merged <- merged %>% group_by(year) %>% 
#   mutate(q05_in  = quantile(in_deg,  0.05, na.rm = TRUE), 
#          q05_out = quantile(out_deg, 0.05, na.rm = TRUE),
#     low_node = as.integer(in_deg <= q05_in & out_deg <= q05_out)) %>% ungroup()

# unique(merged$country[merged$year == 2006 & merged$low_node == 1])
```
```{r}
# length(unique(merged$country[merged$year == 2006 & merged$low_node == 1]))

# colnames(merged)
```





### Plotting the networks

```{r}
nets <- cp_results

nets[["2005"]]$network
nets[["2005"]]$sigma

net_list <- list( n1990 = nets[["1990"]]$network, n2000 = nets[["2000"]]$network, n2010 = nets[["2010"]]$network, n2020 = nets[["2020"]]$network)
```


```{r}
# Filtering the networks based on edge weight. I am keeping only the top 5% of the edges. 
filter_network <- function(g, p = 0.95) {
  thr <- quantile(E(g)$weight, probs = p, na.rm = TRUE)
  g <- delete_edges(g, E(g)[weight < thr])
  g <- delete_vertices(g, V(g)[degree(g) == 0])
  V(g)$strength <- strength(g, mode = "all", weights = E(g)$weight)
  return(g)}
```

```{r}
nets_filtered <- lapply(net_list, filter_network, p = 0.95)
```

```{r}
define_hubs <- function(g) {
  cutoff <- quantile(V(g)$strength, 0.90, na.rm = TRUE)
  V(g)$label <- ifelse(V(g)$strength >= cutoff, V(g)$name, NA)
  return(g)}
```

```{r}
nets_filtered <- lapply(nets_filtered, define_hubs)

n1990_f <- nets_filtered[["n1990"]]
n2000_f <- nets_filtered[["n2000"]]
n2010_f <- nets_filtered[["n2010"]]
n2020_f <- nets_filtered[["n2020"]]
```

```{r}
add_corridor <- function(g, cp_data, yr) {

  ## Core-periphery classification for one year
  cp_year <- cp_data %>%
    filter(year == yr) %>%
    select(country, in_cp)

  ## Edge list from igraph
  edges <- igraph::as_data_frame(g, what = "edges")

  ## Join origin CP
  edges <- edges %>%
    left_join(cp_year,
              by = c("from" = "country")) %>%
    rename(in_cp_origin = in_cp)

  ## Join destination CP
  edges <- edges %>%
    left_join(cp_year,
              by = c("to" = "country")) %>%
    rename(in_cp_destination = in_cp)

  ## Corridor
  edges <- edges %>%
    mutate(
      corridor = case_when(
        in_cp_origin == 0 & in_cp_destination == 0 ~ "PP",
        in_cp_origin == 1 & in_cp_destination == 0 ~ "CP",
        in_cp_origin == 0 & in_cp_destination == 1 ~ "PC",
        in_cp_origin == 1 & in_cp_destination == 1 ~ "CC",
        TRUE ~ NA_character_
      )
    )

  return(edges)
}
```

```{r}
edges1990 <- add_corridor(n1990_f, cp_data, 1990)
edges2000 <- add_corridor(n2000_f, cp_data, 2000)
edges2010 <- add_corridor(n2010_f, cp_data, 2010)
edges2020 <- add_corridor(n2020_f, cp_data, 2020)
```

```{r}
class(n1990_f)
methods(as.data.frame)
```

```{r}
cp_data$country <- dplyr::recode(
  cp_data$country,
  "Russian Federation" = "Russia"
)

edges1990$from <- dplyr::recode(edges1990$from,
                                "Russian Federation" = "Russia")
edges1990$to <- dplyr::recode(edges1990$to,
                              "Russian Federation" = "Russia")

edges2000$from <- dplyr::recode(edges2000$from,
                                "Russian Federation" = "Russia")
edges2000$to <- dplyr::recode(edges2000$to,
                              "Russian Federation" = "Russia")

edges2010$from <- dplyr::recode(edges2010$from,
                                "Russian Federation" = "Russia")
edges2010$to <- dplyr::recode(edges2010$to,
                              "Russian Federation" = "Russia")

edges2020$from <- dplyr::recode(edges2020$from,
                                "Russian Federation" = "Russia")
edges2020$to <- dplyr::recode(edges2020$to,
                              "Russian Federation" = "Russia")
```



```{r}
############################################################
## CHUNK 1 : PREPARE THE WORLD MAP (Run only once)
############################################################

## Read Natural Earth map
world <- rnaturalearth::ne_countries(
  scale = "medium",
  returnclass = "sf"
)

## Representative point inside each country
## (better than centroid for plotting labels)
label_points <- suppressWarnings(
  sf::st_point_on_surface(world)
)

coords <- cbind(
  sf::st_drop_geometry(world),
  sf::st_coordinates(label_points)
)

colnames(coords)[colnames(coords) == "X"] <- "lon"
colnames(coords)[colnames(coords) == "Y"] <- "lat"

## ---------------------------------------------------------
## Harmonize country names between your data and Natural Earth
## ---------------------------------------------------------

coords$country <- coords$name

country_lookup <- c(

  "United States" = "United States of America",
  "Russian Federation" = "Russia",
  "Czech Republic" = "Czechia",
  "Korea, Rep." = "South Korea",
  "Korea, Dem. Rep." = "North Korea",
  "Slovak Republic" = "Slovakia",
  "Syrian Arab Republic" = "Syria",
  "Lao PDR" = "Laos",
  "Viet Nam" = "Vietnam",
  "Iran, Islamic Rep." = "Iran",
  "Egypt, Arab Rep." = "Egypt",
  "Yemen, Rep." = "Yemen",
  "Gambia, The" = "Gambia",
  "Bahamas, The" = "Bahamas",
  "Kyrgyz Republic" = "Kyrgyzstan",
  "Brunei Darussalam" = "Brunei",
  "Congo, Dem. Rep." = "Democratic Republic of the Congo",
  "Congo, Rep." = "Republic of the Congo",
  "Venezuela, RB" = "Venezuela",
  "Micronesia, Fed. Sts." = "Federated States of Micronesia",
  "St. Lucia" = "Saint Lucia",
  "St. Vincent and the Grenadines" = "Saint Vincent and the Grenadines",
  "Antigua and Barbuda" = "Antigua and Barb.",
  "Eswatini" = "eSwatini",
  "Türkiye" = "Turkey"

)

## Apply lookup
coords$country <- dplyr::recode(
  coords$country,
  !!!country_lookup
)

world$country <- world$name

world$country <- dplyr::recode(
  world$country,
  !!!country_lookup
)

## ---------------------------------------------------------
## Keep only what we need later
## ---------------------------------------------------------

coords <- coords %>%
  select(country, lon, lat)

world <- world %>%
  select(country, geometry)

############################################################
## Diagnostic:
############################################################

cat("Countries in map:", nrow(coords), "\n")

cat("Countries in CP data:",
    length(unique(cp_data$country)),
    "\n")

cat("Countries in filtered graph:",
    length(unique(c(edges1990$from, edges1990$to))),
    "\n")

############################################################
## Which countries in the graph are NOT found in the map?
############################################################

setdiff(
  unique(c(edges1990$from, edges1990$to)),
  coords$country
)
```
```{r}
character(0)
```
```{r}
############################################################
## CHUNK 2 : PREPARE THE DATA FOR ONE YEAR
############################################################

prepare_world_network <- function(edges,
                                  cp_data,
                                  world,
                                  coords,
                                  plot_year){

  ##########################################################
  ## Core-periphery classification
  ##########################################################

  cp_year <- cp_data %>%
    filter(year == plot_year) %>%
    distinct(country, .keep_all = TRUE) %>%
    select(country, in_cp)

  ##########################################################
  ## World polygons
  ##########################################################

  world_plot <- world %>%
    left_join(cp_year, by = "country") %>%
    mutate(
      status = case_when(
        is.na(in_cp) ~ "Other",
        in_cp == 1 ~ "Core",
        TRUE ~ "Periphery"
      )
    )

  ##########################################################
  ## Add coordinates to edge origins
  ##########################################################

  edge_plot <- edges %>%
    left_join(
      coords,
      by = c("from" = "country")
    ) %>%
    rename(
      lon1 = lon,
      lat1 = lat
    )

  ##########################################################
  ## Add coordinates to edge destinations
  ##########################################################

  edge_plot <- edge_plot %>%
    left_join(
      coords,
      by = c("to" = "country")
    ) %>%
    rename(
      lon2 = lon,
      lat2 = lat
    )

  ##########################################################
  ## Remove edges without coordinates
  ##########################################################

  edge_plot <- edge_plot %>%
    filter(
      !is.na(lon1),
      !is.na(lat1),
      !is.na(lon2),
      !is.na(lat2)
    )

  ##########################################################
  ## Corridor order
  ##########################################################

  edge_plot$corridor <- factor(
    edge_plot$corridor,
    levels = c("PP","CP","PC","CC")
  )

  ##########################################################
  ## Labels (countries appearing in the filtered graph)
  ##########################################################

  labels <- coords %>%
    semi_join(
      bind_rows(
        edge_plot %>% select(country = from),
        edge_plot %>% select(country = to)
      ),
      by = "country"
    )

  ##########################################################

  list(
    world = world_plot,
    labels = labels,
    edges = edge_plot
  )

}
```


```{r}
net1990 <- prepare_world_network(
  edges1990,
  cp_data,
  world,
  coords,
  1990
)

net2000 <- prepare_world_network(
  edges2000,
  cp_data,
  world,
  coords,
  2000
)

net2010 <- prepare_world_network(
  edges2010,
  cp_data,
  world,
  coords,
  2010
)

net2020 <- prepare_world_network(
  edges2020,
  cp_data,
  world,
  coords,
  2020
)
```

```{r}
## Create the arc data once for debugging

arc_list <- vector("list", nrow(net1990$edges))

for(i in seq_len(nrow(net1990$edges))){

  inter <- tryCatch(
    geosphere::gcIntermediate(
      c(net1990$edges$lon1[i], net1990$edges$lat1[i]),
      c(net1990$edges$lon2[i], net1990$edges$lat2[i]),
      n = 80,
      addStartEnd = TRUE,
      breakAtDateLine = TRUE
    ),
    error = function(e) NULL
  )

  if(is.null(inter)) next

  if(is.list(inter))
    inter <- do.call(rbind, inter)

  arc_list[[i]] <- data.frame(
    lon = inter[,1],
    lat = inter[,2],
    group = i,
    corridor = net1990$edges$corridor[i],
    weight = net1990$edges$weight[i]
  )
}

arcs <- dplyr::bind_rows(arc_list)
```

```{r}
head(arcs)

#summary(arcs$weight)
#table(arcs$corridor)
nrow(arcs)
#str(arcs)
```
```{r}
summary(arcs$lon)
summary(arcs$lat)
sum(is.na(arcs$lon))
sum(is.na(arcs$lat))
range(arcs$weight)
summary(arcs$weight)
```




```{r}
str(net1990)
```
```{r}
head(net1990$edges)
```
```{r}
nrow(net1990$labels)

length(unique(net1990$labels$country))

nrow(net1990$world)
```
```{r}
table(cp_data$in_cp[cp_data$year == 1990])
```
```{r}
arc_split <- split(arcs, arcs$group)

line_geom <- lapply(arc_split, function(x) {
  st_linestring(as.matrix(x[, c("lon", "lat")]))
})

edge_sf <- st_sf(
  corridor = sapply(arc_split, function(x) x$corridor[1]),
  weight   = sapply(arc_split, function(x) x$weight[1]),
  geometry = st_sfc(line_geom, crs = 4326)
)
```

## Countries
geom_sf(...)

## Edges
geom_sf(...)

## Labels
geom_text(...)


```{r}
##########################################################
## Build great-circle arcs
##########################################################

arc_list <- list()

k <- 1

for(i in seq_len(nrow(net$edges))){

  inter <- tryCatch(

    geosphere::gcIntermediate(

      p1 = c(net$edges$lon1[i], net$edges$lat1[i]),
      p2 = c(net$edges$lon2[i], net$edges$lat2[i]),

      n = 80,
      addStartEnd = TRUE,
      breakAtDateLine = TRUE

    ),

    error = function(e) NULL

  )

  ## skip failed edges
  if(is.null(inter))
    next

  ########################################################
  ## Dateline crossing
  ########################################################

  if(is.list(inter)){

    for(j in seq_along(inter)){

      if(is.null(inter[[j]]))
        next

      if(nrow(inter[[j]]) < 2)
        next

      arc_list[[k]] <- list(

        coords = inter[[j]],

        corridor = net$edges$corridor[i],

        weight = net$edges$weight[i]

      )

      k <- k + 1

    }

  }else{

    if(nrow(inter) < 2)
      next

    arc_list[[k]] <- list(

      coords = inter,

      corridor = net$edges$corridor[i],

      weight = net$edges$weight[i]

    )

    k <- k + 1

  }

}
```



```{r}
p1990 <- plot_world_network(net1990, "1990")

p2000 <- plot_world_network(net2000, "2000")

p2010 <- plot_world_network(net2010, "2010")

p2020 <- plot_world_network(net2020, "2020")
```

```{r}
sum(sapply(arc_list, is.null))
```

```{r}
arcs <- bind_rows(arc_list)
```

```{r}
head(arcs)
```

```{r}
table(sapply(arc_list, function(x) is.null(x$coords)))
```




```{r}
world$country[grep("Russia", world$country, ignore.case = TRUE)]
```

```{r}
unique(cp_data$country[grep("Russia", cp_data$country)])
```
```{r}
country_lookup <- c(
  "Russian Federation" = "Russia",
  "United States of America" = "United States of America",
  "Viet Nam" = "Vietnam",
  "Iran (Islamic Republic of)" = "Iran",
  "Syrian Arab Republic" = "Syria",
  "Republic of Korea" = "South Korea")
```

```{r}
cp_data$country <-
    dplyr::recode(cp_data$country,
                  !!!country_lookup)
```












```{r}
p1990 <- plot_world_network(
  edges1990,
  cp_data,
  1990,
  "1990"
)

p2000 <- plot_world_network(
  edges2000,
  cp_data,
  2000,
  "2000"
)

p2010 <- plot_world_network(
  edges2010,
  cp_data,
  2010,
  "2010"
)

p2020 <- plot_world_network(
  edges2020,
  cp_data,
  2020,
  "2020"
)
```


```{r}
colnames(edges1990)
```



```{r}
class(n1990_f)
length(V(n2000_f))
nrow(cp_results[["2000"]]$sigma)
```
For visualization purposes, we use total weighted degree centrality (in+out strength) to capture overall network prominence, while directional centrality measures are reserved for econometric analysis

```{r}
cp_results[["1990"]]$sigma$in_cp
```

```{r}
V(g)$name
```























```{r}
all_strengths <- unlist(lapply(nets_filtered, function(g) strength(g, mode = "in", weights = E(g)$weight)))
all_weights   <- unlist(lapply(nets_filtered, function(g) E(g)$weight))
```





```{r}
plot_network <- function(g, year, cp_results, title_text) {

  # Retrieve CP classification for this year
  sigma <- cp_results[[as.character(year)]]$sigma

  # Match countries in the filtered graph to sigma dataframe
  V(g)$in_cp <- sigma$in_cp[match(V(g)$name, sigma$country)]
  # Label only core countries
  V(g)$label <- ifelse(V(g)$in_cp == 1,V(g)$name,NA)

  ggraph(g, layout = "on_sphere") +
    geom_edge_link(aes(width = weight),alpha = 0.1,show.legend = FALSE) +
    geom_node_point(aes(size = strength,color = factor(in_cp)),alpha = 0.8,show.legend = FALSE) +
    geom_node_text(aes(label = label),repel = TRUE,size = 3,na.rm = TRUE) +
    scale_color_manual(values = c(
        "0" = "#9fc5e8",     
        "1" = "#c9733b")) +
    scale_size(range = c(0.6, 6),limits = range(all_strengths)) +
    scale_edge_width(range = c(0.1, 1.5),limits = range(all_weights)) +
    ggtitle(title_text) +
    theme_void() +
    theme(plot.title = element_text(hjust = 0.5,face = "bold"),legend.position = "none")
}
```

```{r}
library(rnaturalearth)

world <- ne_countries(scale = "medium", returnclass = "sf")

head(world[, c("name", "iso_a3")])
```






```{r}
plot_world_network <- function(g,
                               year,
                               cp_results,
                               title_text,
                               all_strengths,
                               all_weights){

  ##------------------------------------------
  ## Core-periphery classification
  ##------------------------------------------

  sigma <- cp_results[[as.character(year)]]$sigma

  V(g)$in_cp <- sigma$in_cp[
    match(V(g)$name, sigma$country)
  ]

  V(g)$label <- ifelse(
    V(g)$in_cp == 1,
    V(g)$name,
    NA
  )

  ##------------------------------------------
  ## Node dataframe
  ##------------------------------------------

  nodes <- data.frame(
    country  = V(g)$name,
    strength = V(g)$strength,
    in_cp    = V(g)$in_cp,
    label    = V(g)$label,
    stringsAsFactors = FALSE
  )

  ##------------------------------------------
  ## World map
  ##------------------------------------------

  world <- rnaturalearth::ne_countries(
    scale = "medium",
    returnclass = "sf"
  )
  
  

  world$iso3 <- world$iso_a3

  nodes$iso3 <- countrycode(
    nodes$country,
    origin = "country.name",
    destination = "iso3c"
  )

  coords <-
    world |>
    sf::st_point_on_surface()

  coords <- data.frame(
    iso3 = world$iso3,
    st_coordinates(centroids)
  )

  names(coords)[2:3] <- c("lon","lat")

  nodes <- left_join(nodes,
                     coords,
                     by = "iso3")

  ##------------------------------------------
  ## Edge dataframe
  ##------------------------------------------

  edges <- igraph::as_data_frame(g, what = "edges")

  edges <- edges |>
    left_join(nodes |> select(country, lon, lat),
              by = c("from" = "country")) |>
    rename(lon1 = lon,
           lat1 = lat)

  edges <- edges |>
    left_join(nodes |> select(country, lon, lat),
              by = c("to" = "country")) |>
    rename(lon2 = lon,
           lat2 = lat)

  ##------------------------------------------
  ## Great-circle paths
  ##------------------------------------------

  edge_paths <- lapply(seq_len(nrow(edges)), function(i){

    if(any(is.na(edges[i,c("lon1","lat1","lon2","lat2")])))
      return(NULL)

    gc <- geosphere::gcIntermediate(
      c(edges$lon1[i], edges$lat1[i]),
      c(edges$lon2[i], edges$lat2[i]),
      n = 80,
      addStartEnd = TRUE,
      sp = FALSE
    )

    data.frame(
      lon = gc[,1],
      lat = gc[,2],
      id = i,
      weight = edges$weight[i]
    )

  })

  edge_paths <- bind_rows(edge_paths)

  ##------------------------------------------
  ## Plot
  ##------------------------------------------

  ggplot() +

    geom_sf(
      data = world,
      fill = "grey96",
      colour = "grey75",
      linewidth = 0.2
    ) +

    geom_path(
      data = edge_paths,
      aes(lon,
          lat,
          group = id,
          linewidth = weight),
      colour = "grey45",
      alpha = 0.20,
      lineend = "round"
    ) +

    geom_point(
      data = nodes,
      aes(lon,
          lat,
          size = strength,
          fill = factor(in_cp)),
      shape = 21,
      colour = "black",
      stroke = .25,
      alpha = .90
    ) +

    ggrepel::geom_text_repel(
      data = subset(nodes, !is.na(label)),
      aes(lon,
          lat,
          label = label),
      size = 3,
      max.overlaps = Inf
    ) +

    scale_fill_manual(values = c(
      "0" = "#9fc5e8",
      "1" = "#c9733b"
    )) +

    scale_size(
      range = c(0.6,6),
      limits = range(all_strengths)
    ) +

    scale_linewidth(
      range = c(0.1,1.5),
      limits = range(all_weights)
    ) +

    coord_sf(expand = FALSE) +

    ggtitle(title_text) +

    theme_void() +

    theme(
      plot.title = element_text(
        hjust = .5,
        face = "bold"
      ),
      legend.position = "none"
    )

}
```

```{r}
p1990 <- plot_world_network(
  n1990_f,
  year = 1990,
  cp_results = cp_results,
  title_text = "1990",
  all_strengths = all_strengths,
  all_weights = all_weights
)

p2000 <- plot_world_network(
  n2000_f,
  2000,
  cp_results,
  "2000",
  all_strengths,
  all_weights
)

p2010 <- plot_world_network(
  n2010_f,
  2010,
  cp_results,
  "2010",
  all_strengths,
  all_weights
)

p2020 <- plot_world_network(
  n2020_f,
  2020,
  cp_results,
  "2020",
  all_strengths,
  all_weights
)
```
```{r}
p2020
```








```{r}
#find.package("rnaturalearth", quiet = TRUE)
#installed.packages()[c("rnaturalearth","rnaturalearthdata"), c("Package","Version")]
```

```{r}
install.packages("rnaturalearthdata", repos = "https://cloud.r-project.org", dependencies = TRUE)
```
```{r}
.rs.restartR()
```

```{r}
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(countrycode)
library(geosphere)
```
```{r}
world <- rnaturalearth::ne_countries(
    scale = "medium",
    returnclass = "sf"
)

plot(sf::st_geometry(world))
```




























```{r}
library(igraph)
library(ggraph)
library(ggplot2)

plot_network <- function(g, year, cp_results, title_text, all_strengths, all_weights,
                         r_core = 0.05, r_min = 0.3, r_max = 1) {

  sigma_df <- cp_results[[as.character(year)]]$sigma
  V(g)$in_cp <- sigma_df$in_cp[match(V(g)$name, sigma_df$country)]
  # if sigma_in column name differs, change below:
  sigma_in <- sigma_df$sigma_in[match(V(g)$name, sigma_df$country)]

  # fallback if sigma_in missing
  if (is.null(sigma_in)) sigma_in <- rep(0, vcount(g))

  V(g)$label <- ifelse(V(g)$in_cp == 1, V(g)$name, NA)

  # scale sigma_in 0..1
  s_scaled <- (sigma_in - min(sigma_in, na.rm = TRUE)) /
              (diff(range(sigma_in, na.rm = TRUE)) + .Machine$double.eps)

  # radius: cores near center, peripherals mapped by sigma_in
  radius <- ifelse(V(g)$in_cp == 1,
                   runif(sum(V(g)$in_cp == 1), 0, r_core),         # small jitter for cores
                   r_min + s_scaled * (r_max - r_min))

  # angles
  theta <- runif(vcount(g), 0, 2 * pi)

  coords <- data.frame(x = radius * cos(theta),
                       y = radius * sin(theta),
                       name = V(g)$name)

  # create manual layout so ggraph uses these coords in correct order
  layout <- create_layout(g, layout = "manual", x = coords$x, y = coords$y)

  ggraph(layout) +
    geom_edge_link(aes(width = weight), alpha = 0.12, show.legend = FALSE) +
    geom_node_point(aes(size = strength, color = factor(in_cp)), alpha = 0.9, show.legend = FALSE) +
    geom_node_text(aes(label = label), repel = TRUE, size = 3, na.rm = TRUE) +
    scale_color_manual(values = c("0" = "grey70", "1" = "#1F4E79")) +
    scale_size(range = c(0.6, 6), limits = range(all_strengths)) +
    scale_edge_width(range = c(0.1, 1.5), limits = range(all_weights)) +
    ggtitle(title_text) +
    theme_void() +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"),
          legend.position = "none")
}

```

```{r}
# plot_network <- function(g, year, cp_results, title_text) {
# 
#   # Retrieve CP results for the year
#   sigma <- cp_results[[as.character(year)]]$sigma
# 
#   # Match CP measures to network vertices
#   V(g)$in_cp <- sigma$in_cp[
#     match(V(g)$name, sigma$country)
#   ]
# 
#   V(g)$sigma_in <- sigma$sigma_in[
#     match(V(g)$name, sigma$country)
#   ]
# 
#   # Strength
#   V(g)$strength <- strength(
#     g,
#     mode = "all",
#     weights = E(g)$weight
#   )
# 
#   # Label only core countries
#   V(g)$label <- ifelse(
#     V(g)$in_cp == 1,
#     V(g)$name,
#     NA
#   )
# 
#   # Continuous coreness → radius (higher sigma = closer center)
#   coreness <- V(g)$sigma_in
# 
#   radius <- scales::rescale(
#     1 - coreness,
#     to = c(0.05, 1)
#   )
# 
#   # Spread nodes around the circle
#   theta <- seq(
#     0,
#     2 * pi,
#     length.out = vcount(g) + 1
#   )[-(vcount(g) + 1)]
# 
#   coords <- cbind(
#     radius * cos(theta),
#     radius * sin(theta)
#   )
# 
#   # Plot
#   ggraph(
#     g,
#     layout = "manual",
#     x = coords[, 1],
#     y = coords[, 2]
#   ) +
# 
#     geom_edge_link(
#       aes(width = weight),
#       alpha = 0.08,
#       colour = "grey60",
#       show.legend = FALSE
#     ) +
# 
#     geom_node_point(
#       aes(
#         size = sigma_in,
#         color = factor(in_cp)
#       ),
#       alpha = 0.85,
#       show.legend = FALSE
#     ) +
# 
#     geom_node_text(
#       aes(label = label),
#       repel = TRUE,
#       size = 3,
#       na.rm = TRUE
#     ) +
# 
#     scale_color_manual(
#       values = c(
#         "0" = "grey70",
#         "1" = "#1F4E79"
#       )
#     ) +
# 
#     scale_size_continuous(
#       range = c(2, 12),
#       trans = "sqrt"
#     ) +
# 
#     scale_edge_width(
#       range = c(0.1, 1.5)
#     ) +
# 
#     ggtitle(title_text) +
# 
#     theme_void() +
# 
#     theme(
#       plot.title = element_text(
#         hjust = 0.5,
#         face = "bold",
#         size = 12
#       ),
#       legend.position = "none"
#     )
# }
```


```{r}
# compute node strengths for this graph (used inside plotting too)
strengths_1990 <- strength(n1990_f, weights = E(n1990_f)$weight)

# if you want global ranges across multiple years, combine them; otherwise use per-year:
all_strengths <- strengths_1990           # or c(strengths_1990, strengths_1991, ...)
all_weights <- E(n1990_f)$weight          # or c(E(g1)$weight, E(g2)$weight, ...)

# call with defaults for radii
p1990 <- plot_network(n1990_f,
                      year = 1990,
                      cp_results = cp_results,
                      title_text = "1990",
                      all_strengths = all_strengths,
                      all_weights = all_weights)

# example with custom radii
p1990b <- plot_network(n1990_f, 1990, cp_results, "1990",
                       all_strengths, all_weights,
                       r_core = 0.02, r_min = 0.25, r_max = 1.2)

```



```{r}
p1990
```


```{r}
p1990b
```






```{r}
p1990 <- plot_network(n1990_f,year = 1990,cp_results = cp_results,title_text = "1990")
p2000 <- plot_network(n2000_f,year = 2000,cp_results = cp_results,title_text = "2000")
p2010 <- plot_network(n2010_f,year = 2010,cp_results = cp_results,title_text = "2010")
p2020 <- plot_network(n2020_f,year = 2020,cp_results = cp_results,title_text = "2020")
```

```{r}
p1990 
```
```{r}
p2020
```
```{r}
sigma2020 <- cp_results[["2020"]]$sigma

sigma2020[
  sigma2020$country %in% c(
    "Ukraine",
    "United States of America",
    "Germany",
    "France",
    "India",
    "United Kingdom"
  ),
  c("country", "sigma_in", "in_cp")
]
```





```{r}
p_footer <- ggplot(data.frame(x = c(1,2,3,4),y = c(1,1,1,1),cp = c("Core","Periphery","Core","Periphery"),strength = c(1e6,1e6,5e6,5e6)),
  aes(x = x, y = y)) +
  geom_point(aes(color = cp, size = strength),alpha = 0) +
  scale_color_manual(values = c("Core" = "#1F4E79","Periphery" = "grey70"),name = "Position:") +
  scale_size(range = c(0.6, 6),limits = range(all_strengths),name = "Node Strength:",labels = scales::label_number(scale_cut = scales::cut_short_scale())) +
  theme_void() +
  guides(color = guide_legend(nrow = 1,order = 1,override.aes = list(alpha = 0.8,size = 5)),
    size = guide_legend(nrow = 1,order = 2,override.aes = list(alpha = 0.8,color = "grey40"))) +
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.direction = "horizontal",
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 10),
    legend.spacing.x = unit(1.5, "cm"),
    legend.box.spacing = unit(0.1, "cm")
  )

```

```{r}
network_grid <- wrap_plots(
  p1990 + ggtitle("1990"),
  p2000 + ggtitle("2000"),
  p2010 + ggtitle("2010"),
  p2020 + ggtitle("2020"),
  ncol = 2
)
```



```{r}
exists("network_grid")
exists("p_footer")
exists("p1990")
exists("p2000")
exists("p2010")
exists("p2020")
```
```{r}
figure2 <- network_grid /
  p_footer +
  plot_layout(heights = c(12, 1))

figure2
```
Blue nodes indicate core countries identified by the weighted core–periphery algorithm; gray nodes indicate peripheral countries. Node size is proportional to weighted degree centrality. Only the strongest migration corridors (top 5% of edge weights) are displayed.
```{r}
class(p1990)
class(p2000)
class(p2010)
class(p2020)
```


```{r}
ggsave("../outputs/Fig3.tiff",figure2,width = 12,height = 12,dpi = 600)
```


























